---
title: "Simulation example"
output: html_notebook
---


Determine whether we use the churn or the sales convention for our target variable. In the churn convention, a persuadable customer is such that $Y_0=1$ and $Y_1=0$, while in the sales convention, it is $Y_0=0$ and $Y_1=1$.
```{r}
library(ggplot2)

source("simulation.R")
source("eval_measures.R")

use_churn_convention <- TRUE
```


The first approach uses bivariate beta distribution from "Olkin, Ingram, and Thomas A. Trikalinos. "Constructions for a bivariate beta distribution." Statistics & Probability Letters 96 (2015): 54-60.". Using the causal classification matrix, we know that the distribution of $S_0$ and $S_1$ should respect
\[\beta = \mathbb E[S_0](1- \mathbb E[S_1]) - \mathrm{cov}(S_0, S_1)\]
\[\delta = \mathbb E[S_0]\mathbb E[S_1] + \mathrm{cov}(S_0, S_1)\]
\[\gamma = (1-\mathbb E[S_0])\mathbb E[S_1] - \mathrm{cov}(S_0, S_1)\]
The distribution of $S_0$ and $S_1$ is defined such that $S_0 = U_{11} + U_{10}$ and $S_1 = U_{11} + U_{01}$ where $U_{00}, U_{01}, U_{10}, U_{11}$ form a Dirichlet distribution of parameters $a=[a_{00},a_{01},a_{10},a_{11}]$.
We can derive the value of $\mathbb E[S_0]$, $\mathbb E[S_1]$ and $\mathrm{cov}(S_0, S_1)$ as functions of $a$, and derive the value of $a$ from $\beta, \gamma, \delta$ using the system of three equations above. Since there are four parameters in $a$, we can set $a_{00}+a_{01}+a_{10}+a_{11} = 1$.


First, let's make a test for a specific value of $\beta, \gamma, \delta$:
```{r}
alpha <- 0.8
beta <- 0.1
gamma <- 0.05
delta <- 1 - alpha - beta - gamma

v <- beta * gamma - alpha * delta
min_A <- max(v / min(alpha, delta), -v / min(beta, gamma))
cat("Make sure that A > ", min_A, "\n")

sd_noise <- 0.2
A <- 2

data <- sample_bivariate_beta(
  beta, gamma, delta,
  N = 5000,
  proba_treatment = 0.65,
  A = A,
  noise_S_0 = sd_noise,
  noise_S_1 = sd_noise,
  use_churn_convention = use_churn_convention
)
```

Compute causal precision curves of both churn and uplfit approaches (with non-null variance) and plot the curve
```{r}
steps <- 100

curve_c <- causal_precision_curve(
  data$S_0_hat,
  data$S_0,
  data$S_1,
  n_steps = steps,
  use_churn_convention = use_churn_convention
)

curve_u <- causal_precision_curve(
  data$uplift_hat,
  data$S_0,
  data$S_1,
  n_steps = steps,
  use_churn_convention = use_churn_convention
)

curve_c$Approach <- "ML"
curve_u$Approach <- "Uplift"


ggplot(rbind(curve_c, curve_u)) +
  geom_smooth(
    aes(x = threshold, y = precision, color = Approach, linetype = Approach),
    method = "gam", formula = y ~ s(x, bs = "cs", k = 50), fill = NA, size = 0.6) +
  labs(x = "Customers in campaign (%)", y = "Causal precision") +
  theme_bw()
```

And also the uplift curve
```{r}
uplift_curve_u <- true_uplift_curve(data$uplift_hat, data$uplift, use_churn_convention = use_churn_convention)
uplift_curve_c <- true_uplift_curve(data$S_0_hat, data$uplift, use_churn_convention = use_churn_convention)
uplift_curve_u$Approach <- "Uplift"
uplift_curve_c$Approach <- "ML"

ggplot(rbind(uplift_curve_u, uplift_curve_c),
       aes(x = 100 * normalized_x, y = 100 * normalized_uplift, color = Approach, linetype = Approach)) +
  # Add the diagonal line
  geom_segment(x = 0, y = 0,
               xend = 100, yend = max(100 * grid$normalized_uplift[grid$n == max(grid$n)]),
               colour = "#AAAAAA", show.legend = FALSE
              ) +
  geom_line() +
  labs(x = "Targeted customers (%)", y = "Uplift (%)") +
  theme_bw()
```

We can also visualize the distribution of scores and causal class in a scatter plot

```{r}
if (use_churn_convention) {
  cust_type_labels <- c("Sure thing", "Do-not-disturb", "Persuadable", "Lost cause")
} else {
  cust_type_labels <- c("Lost cause", "Persuadable", "Do-not-disturb", "Sure thing")
}
ggplot(data, aes(x = S_0, y = S_1, color = paste0(Y_0, Y_1))) +
  geom_point(alpha = 0.5) +
  scale_color_discrete(name = "Customer type", labels = cust_type_labels)
```
